Stimjim: open source hardware for precise electrical stimulation

### 2019-05-10 benchmarking/paper/draft2.Rnw
updates to benchmarking analysis

getPulseParams = function(f, thresh=25, fs, vpau){

  dat = matrix(readBin(f, what='integer', n=1e7, size=2, endian = 'big'),ncol=2,byrow=TRUE)

@@

par(mar=c(4,5,2,2), mfrow=c(4,3))

plotParams = list(
   list(j=1:30, column=3, label='Inter-pulse interval'),
   list(j=31:60, column=5, label='Inter-pulse interval'),
   list(j=61:90, column=7, label='Inter-pulse interval'))

for (i in 1:3){
  with(plotParams[[i]], {
    x = paramMat[j,column];

    plot(x, sapply(res[j], function(x) x$IPI.summary[3])*1e6, xlab=paste(label, "setting"), ylab=paste("Measured median",label), log='xy')
    plot(x, sapply(res[j], function(x) x$IPI.sd)*1e6,         xlab=paste(label, "setting"), ylab=paste("Measured median",label), log='xy')
    plot(x, sapply(res[j], function(x) x$IPI.sd)*1e6,         xlab=paste(label, "setting"), ylab=paste("Measured median",label), log='xy')
  })
}
@

>>>>

getPulseParams = function(f, thresh=25, fs, vpau){
  dat = matrix(readBin(f, what='integer', n=1e7, size=2, endian = 'big'),ncol=2,byrow=TRUE)

@@

par(mar=c(4,5,2,2), mfrow=c(4,3))
#matplot(sapply(res[1:60], function(x) x$pulseMat[,1]), col=c(1,2), type='l', lty=1)
plot(paramMat[1:30,3], sapply(res[seq(1,60,by=2)], function(x) x$IPI.summary[3])*1e6, 
  log='xy', main='median IPI vs target', cex=0.75, xlab='Target IPI', ylab='Median measured IPI')
points(paramMat[1:30,3], sapply(res[seq(2,60,by=2)], function(x) x$IPI.summary[3])*1e6,
  col='red', cex=0.75)
abline(a=0,b=1)

#matplot(dendRites::offset(sapply(res[61:120], function(x) x$pulseMat[,1])), col=c(1,2), type='l', lty=1)
plot(paramMat[1:30,3], sapply(res[seq(1,60,by=2)], function(x) x$IPI.sd)*1e6, 
  log='x', main='IPI sd', cex=0.75, xlab='Target IPI', ylab='Measured IPI std. dev.')
points(paramMat[1:30,3], sapply(res[seq(2,60,by=2)], function(x) x$IPI.sd)*1e6,
  col='red', cex=0.75)

plot(paramMat[1:30,3], sapply(res[seq(1,60,by=2)], function(x) diff(x$IPI.summary[c(1,6)]))*1e6, 
  log='x', main='IPI range', cex=0.75, xlab='Target IPI', ylab='Range of measured IPIs')
points(paramMat[1:30,3], sapply(res[seq(2,60,by=2)], function(x) diff(x$IPI.summary[c(1,6)]))*1e6,
  col='red', cex=0.75)

plot(paramMat[31:59,7], sapply(res[seq(61,118,by=2)], function(x) x$PW.summary[3])*1e6/2, 
  log='xy', main='median PW vs target', ylab='measured median PW', cex=0.75)
points(paramMat[31:59,7], sapply(res[seq(62,118,by=2)], function(x) x$PW.summary[3])*1e6/2,
  col='red', cex=0.75)
abline(a=0,b=1)

plot(paramMat[31:59,7], sapply(res[seq(61,118,by=2)], function(x) x$PW.sd)*1e6/2, 
  log='x', main='PW sd', ylab='PW sd', cex=0.75)
points(paramMat[31:59,7], sapply(res[seq(62,118,by=2)], function(x) x$PW.sd)*1e6/2,
  col='red', cex=0.75)

plot(paramMat[31:59,7], sapply(res[seq(61,118,by=2)], function(x) diff(x$PW.summary[c(1,6)]))*1e6/2, 
  log='x', main='PW range', ylab='PW range', cex=0.75)
points(paramMat[31:59,7], sapply(res[seq(62,118,by=2)], function(x) diff(x$PW.summary[c(1,6)]))*1e6/2,
  col='red', cex=0.75)

plot(paramMat[61:90,5], sapply(res[seq(121,180,by=2)], function(x) x$sh.median*1e3), 
  log='', main='amplitude vs target', xlab='Target amplitude (mV)', ylab='measured amplitude (mV)', cex=0.75)
abline(a=0,b=1.0)
points(paramMat[61:90,5], sapply(res[seq(122,180,by=2)], function(x) x$sh.median*1e3),
  col='red', cex=0.75)
